Project Notes

### 2020-04-03 notes/notes.tex
Notes: update 03/04/2020

\item
Now focusing on formalising the React generated 
code -- taking more time than planned because
the TicTacToe example made more assumptions
about the protocol than I thought
\end{itemize}

>>>>

\item
Now focusing on formalising the React generated 
code -- taking more time than planned because
the TicTacToe example made more assumptions
about the protocol than I thought.
\end{itemize}

\paragraph{03/04/2020}
\begin{itemize}
\item
Build system testing pipeline -- register which
Scribble protocols to test, specify which role
(e.g. Bob) corresponds with which target (e.g. Node),
then the pipeline will perform the code generation,
check for success exit code, then invoke the
TypeScript compiler to check the TypeScript code
and also check for success exit code.
\end{itemize}
